\documentclass{curriculum}
\author{Rolf Vidar {\bfseries Mazunki} Hoksaas}
\email{me@mazunki.tech}
\phone{+4748447243}
\github{@mazunki}
\linkedin{@mazunki}
\website{mazunki.dev}
\jobtitle{Software Engineer}
\date{}

\begin{document}
	\maketitle

	\section{Summary}
	\paragraph{} I'm a curious person and developer by nature, so I will dig into anything in order to understand it. I am an active defendant of open source development, and continuously try to search for things to improve. 
	\paragraph{} I have more than average knowledge about many things, making me a great asset anywhere. I combine pieces of knowledge from different places in order to build greater things. That's why I have so many personal projects going on in my free time.

	\section{Skills}
	\subsection{Languages}
	\begin{half}
		\subsubsection{Programming}
			\begin{itemize}
				\item Python, Java
				\item C/C++, GoLang
				\item sed, awk, Bash, sh, RegEx, POSIX...
			\end{itemize}
		\subsubsection{Markup}
			\begin{itemize}
				\item \LaTeX
				\item HTML, CSS3
				\item Tkinter, FXML, GTK3
			\end{itemize}
	\end{half}
	\begin{half}
		\subsubsection{Natural}
			\begin{itemize}
				\item English --- fluent
				\item Spanish --- native
				\item Norwegian --- native
				\item Catalan --- fluent
				\item Esperanto --- intermediate
				\item Japanese --- beginner
			\end{itemize}
	\end{half}

	\subsection{Hands on}
	\begin{itemize} 
		\item Decent knowledge about electronics
		\item Project management skills
		\item Teamwork and workflow
	\end{itemize}	


	\section{Experience}	
	\begin{half}
	\subsection{Work}
		\begin{itemize}
		\item Maritime industry
			\subitem Worked for several years
			\subitem Cargo, passengers, maintenance
		\end{itemize}
	\end{half}
	\begin{half}
	\subsection{Projects}
		\begin{itemize}
			\item TJ Bot
				\subitem An AI-based home device which can make your life easier.
			\item A repository with several linux scripts for my own use.
			\item Currently working on integrating input devices between different platforms I use.
		\end{itemize}
	\end{half}
	\section{Academics}
	\begin{half}
	\subsection{School}
		\begin{itemize}
			\item Robotics and intelligent systems
				\subitem University of Oslo
				\subitem Currently enrolled
			\item Applied Data Science
				\subitem Noroff University
				\subitem One year
		\end{itemize}
	\end{half}
	\begin{half}
	\subsection{Titles}
		\begin{itemize}
			\item Boat Driver License
			\item Crowd- and Crisis Management
			\item Safety Course for seafarers
		\end{itemize}
	\end{half}

\end{document}
